Streaming Fact Extraction for Wikipedia Entities at Web-Scale

### 2013-11-18 paper/flairs27/content/results.tex
get back authors
change machine model to the processor information

\begin{table}
\caption{Benchmark Server Specifications}
\centering
\label{table:serverspec}
\begin{tabular}{| c | p{4.8cm} |}
\hline 
\textbf{Spec} & \textbf{Details} \\ \hline
Model & Dell xxx 32 cores \\ \hline 
OS & CentOS release 6.4 Final \\ \hline 
Software Stack & GCC version 4.4.7, Java 1.7.0\_25, Scala 2.9.2, SBT 0.12.3 \\ \hline 
 RAM & 64GB\\ \hline 
 Drives & 2x2.7TB disks, 6Gbps, 7200RPM\\ \hline 
\end{tabular} 
\end{table}

@@

\begin{tabular}{|p{3.8cm}|p{3cm}|}
\hline 
\textbf{Document Type} & \textbf{\# of Documents}\\ 
\hline 
Arxiv & 10988  \\ \hline
 Classified & 34887  \\ \hline
 Forum & 77674  \\ \hline
 Linking & 12947  \\ \hline
 Mainstream News & 141936  \\ \hline
 Memetracker & 4137  \\ \hline
 News & 280629  \\ \hline
 Review & 6347 \\ \hline
 Social & 688848 \\ \hline
 Weblog & 740987  \\ \hline
\hline 
\end{tabular} 
\end{table}

>>>>

\begin{table}
\caption{Benchmark Server Specifications}
\centering
\label{table:serverspec}
\begin{tabular}{| c | p{4.8cm} |}
\hline 
\textbf{Spec} & \textbf{Details} \\ \hline
Processor & 32 core AMD Opteron\textsuperscript{TM} 6272 \\ \hline 
OS & CentOS release 6.4 Final \\ \hline 
Software Stack & GCC version 4.4.7, Java 1.7.0\_25, Scala 2.9.2, SBT 0.12.3 \\ \hline 
 RAM & 64GB\\ \hline 
 Drives & 2x2.7TB disks, 6Gbps, 7200RPM\\ \hline 
\end{tabular} 
\end{table}

@@

\begin{tabular}{|p{3.8cm}|p{3cm}|}
\hline 
\textbf{Document Type} & \textbf{\# of Documents}\\ 
\hline 
Arxiv & 10988  \\ \hline
 Classified & 34887  \\ \hline
 Forum & 77674  \\ \hline
 Linking & 12947  \\ \hline
 Mainstream News & 141936  \\ \hline
 Memetracker & 4137  \\ \hline
 News & 280629  \\ \hline
 Review & 6347 \\ \hline
 Social & 688848 \\ \hline
 Weblog & 740987  \\ \hline
%\hline 
\end{tabular} 
\end{table}
